MLH1 Results Outline

### 2020-02-05 doc/Main_Report_Results.rmd
new file MERGing MLH1 and bivalent based results

# Models Framework

@@

For now I will focus on 3 different models for comparing the subsp, sex and strain effects across relevant dependant variables.

@@

@@

A general pattern is that the female data has higher within mouse variance (both var and cV). Some strains more than others (invetigate potential outliers). (LEW females with top 3 variance are all from different dissection dates)
This pattern also holds for within mouse cv for MLH1 count (not shown).

@@

### Modeling Within Mouse Variance

@@

@@

@@

@@

$$mouse CO metric  ~=~ subsp * sex * strain + \varepsilon$$

```{r M4.MLH1.var, echo=FALSE}

@@

test a model for fixed effects of strains within musc. The purpose is to distinguihsi musc strains from low 'Dom' level strains.

>>>>

# Average MLH1 Count Model

@@

For now I will focus on 3 different models for comparing the subsp, sex and strain effects across relevant dependent variables.

@@

#### Summary of Mixed models

@@

A general pattern is that the female data has higher within mouse variance (both var and cV). Some strains more than others (investigate potential outliers). (LEW females with top 3 variance are all from different dissection dates)
This pattern also holds for within mouse cv for MLH1 count (not shown).

@@

> Modeling Within Mouse Variance

@@

## MLH1 variance M1

@@

## MLH1 variance M2

@@

```{r M2.MLH1.var, echo=FALSE}

@@

## MLH1 variance M3

$$mouse \ CO \ metric  ~=~ subsp * sex * strain + \varepsilon$$

@@

test a model for fixed effects of strains within musc. The purpose is to distinguish musc strains from low 'Dom' level strains.
